### 2015-05-15 background.tex
fix in figure 2

\begin{figure}[t]
\begin{lstlisting}
static loff_t nvram_llseek(struct file *file,
    loff_t offset, int origin) {
  switch (origin) {
    case 0: break;
    case 1: offset += file->f_pos; break; // racy
    case 2: offset += nvram_len; break;
    default: offset = -1;
  }
  if (offset < 0)
    return -EINVAL;
  file->f_pos = offset; // racy
  return file->f_pos; // racy
}
\end{lstlisting}
\vspace{-2mm}
\caption{Racy entry point in the generic\_nvram Linux driver}
\label{fig:data_race_example}
\vspace{-2mm}
\end{figure}

@@

\begin{figure}[t]
\begin{lstlisting}
static loff_t nvram_llseek(struct file *file,
    loff_t offset, int origin) {
  mutex_lock(&nvram_mutex); // lock
  switch (origin) {
    case 0: break;
    case 1: offset += file->f_pos; break;
    case 2: offset += nvram_len; break;
    default: offset = -1;
  }
  if (offset < 0)
    return -EINVAL;
  file->f_pos = offset;
  loff_t res = file->f_pos; // store result
  mutex_unlock(&nvram_mutex); // unlock
  return res;
}
\end{lstlisting}
\vspace{-2mm}
\caption{Using a lock to eliminate the data races in the previous example}
\label{fig:lock_example}
\vspace{-2mm}
\end{figure}

@@

Figure~\ref{fig:locksets} shows an example of applying lockset analysis on a concurrent program consisting of two threads $T_1$ and $T_2$, both accessing a global variable $A$. Initially, $\mathit{LS}_A$, which is the lockset for A, contains all possible locks in the program: $M$ and $N$. During execution of $T_1$, the thread writes $A$ without holding $N$, and thus $N$ is removed from $\mathit{LS}_A$. Next, during execution of $T_2$, the thread writes $A$ without holding $M$, and thus $\mathit{LS}_A$ becomes empty. As a result, a warning is reported because the two threads do not consistently protect $A$.

>>>>

\begin{figure}[t]
\begin{lstlisting}
static loff_t nvram_llseek(struct file *file,
    loff_t offset, int origin) {
  switch (origin) {
    case 0: break;
    case 1: offset += file->f_pos; break; // racy
    default: offset = -1;
  }
  if (offset < 0) return -EINVAL;
  file->f_pos = offset; // racy
  return file->f_pos; // racy
}
\end{lstlisting}
\vspace{-2mm}
\caption{Racy entry point in the generic\_nvram Linux driver}
\label{fig:data_race_example}
\vspace{-2mm}
\end{figure}

@@

\begin{figure}[t]
\begin{lstlisting}
static loff_t nvram_llseek(struct file *file,
    loff_t offset, int origin) {
  mutex_lock(&nvram_mutex); // lock
  switch (origin) {
    case 0: break;
    case 1: offset += file->f_pos; break;
    default: offset = -1;
  }
  if (offset < 0) {
    mutex_unlock(&nvram_mutex); // unlock
    return -EINVAL;
  }
  file->f_pos = offset;
  loff_t res = file->f_pos; // store result
  mutex_unlock(&nvram_mutex); // unlock
  return res;
}
\end{lstlisting}
\vspace{-2mm}
\caption{Using a lock to eliminate the data races in the previous example}
\label{fig:lock_example}
\vspace{-2mm}
\end{figure}

@@

Figure~\ref{fig:locksets} shows an example of applying lockset analysis to a concurrent program consisting of two threads $T_1$ and $T_2$, both accessing a global variable $A$. Initially, $\mathit{LS}_A$, which is the lockset for A, contains all possible locks in the program: $M$ and $N$. During execution of $T_1$, the thread writes $A$ without holding $N$, and thus $N$ is removed from $\mathit{LS}_A$. Next, during execution of $T_2$, the thread writes $A$ without holding $M$, and thus $\mathit{LS}_A$ becomes empty. As a result, a warning is reported because the two threads do not consistently protect $A$.
